Approximating the Optimal State Abstraction

### 2016-04-30 icml_workshop/framework.tex
beep

In previous work~\cite{abelhershko2016approx}, we extended the unifying framework of state abstraction proposed by~\cite{li2006towards}. In this work we develop a theory of approximate abstraction, in which abstraction is interpreted as state aggregation; that is, a state abstraction function $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$,

Formalism

Extension to Temp Ext

@@

>>>>

In previous work~\cite{abelhershko2016approx}, we extended the unifying framework of state abstraction proposed by~\cite{li2006towards}. We develop a theory of approximate abstraction, in which abstraction is interpreted as state aggregation; that is, a state abstraction function $\phi : \mathcal{S}_G \mapsto \mathcal{S}_A$, induces a full abstract \ac{MDP} according to the methods described by~\cite{li2006towards}.

More formally, we think of abstraction in terms of a state aggregation function mapping ground states of a {\it ground} MDP to abstract states of an {\it abstract} MDP.

We consider several {\it types} of aggregation function families; each of which ensures that all aggregated states are within $\varepsilon$ of one another with respect to some function of interest. The four families are:
\begin{enumerate}
\item $\epQ$: states that are aggregated have similar $Q^*$ values
\item $\epM$: states that are aggregated have similar transition functions and reward functions.
\item $\epMu$: states that are aggregated have similar multinomial distributions over $Q^*$ values.
\item $\epB$: states that are aggregated have similar Boltzmann distributions over $Q^*$ values.
\end{enumerate}

Our main result is that, any instance of any of the above abstraction functions will induce an abstract \ac{MDP} such that, the optimal policy of the abstract MDP, denoted $\pi_A^*$, when used to solve the ground MDP, has value that is within a polynomial of $\varepsilon$ of the true optimal value function. Here, $\varepsilon$ determines how aggressive the abstraction is; for a $\varepsilon=0$, the state aggregation functions will only aggregate states that share exact values.

\begin{thm}
There exist at least four classes of approximate state-aggregation functions, $\epQ$, $\epM$, $\epB$ and $\epMu$, for which the optimal policy in the abstract \ac{MDP}, applied to the ground \ac{MDP}, has suboptimality bounded polynomially in $\frac{1}{\varepsilon}$:
\begin{equation}
\forall_{s \in \mathcal{S}_G} V_G^{\pi_G^*}(s) - V_G^{\pi_{A}^*}(s) \leq poly \left (\frac{1}{\varepsilon} \right).
\end{equation}
\end{thm}

This theorem satisfies the \textsc{Value} desiderata. Moreover, we stipulate that functions of these classes are learnable due to the criteria of $\varepsilon$-closeness, as was demonstrated by~\cite{ortner2007logarithmic}. Furthermore, we empirically demonstrate the compressibility of these functions, and consider it an open problem as to what degree of compressibility is achievable under this framework.

% Subsection: Temporal Abstraction
\subsection{Temporal Abstraction}
Most critically, however, is the framework's natural extension to temporal abstraction. To do so, we consider a pair of functions: $\{\widetilde{\phi}_f, \Delta_g\}$, where:
\begin{equation}
\widetilde{\phi}_f: \mathcal{S}_G \mapsto \mathcal{S}_A, \hspace{16mm} \Delta_g \mathcal{A}_G \mapsto \mathcal{A}_A
\end{equation}

Now, the abstract MDP is fully distinct from $M_G$, in that it also has a unique set of abstract actions. As before, we can prove bounds on the value lost under different {\it kinds} of functions $\Delta_g$, which will provide a clear distinction between which abstract actions can preserve value, and which do not. In the next section, we show some preliminary empirical results to demonstrate how this process works.

@@

\dnote{put epsilon in subscript of phi}

### 2016-04-30 icml_workshop/introduction.tex
beep

% Planning and RL is hard.
For this reason abstraction is of considerable interest in planning and \ac{RL} work~\yrcite{li2006towards,abelhershko2016approx,konidaris2007building,hauskrecht1998hierarchical,parr1998reinforcement,sutton1999between,konidaris2015constructing,Jiang2015,andre2002state}. Planning and \ac{RL} problems tackle solving for optimal behavior in \acp{MDP}.

>>>>

% Planning and RL is hard.
For this reason abstraction is of considerable interest in planning and \ac{RL} work~\yrcite{li2006towards,abelhershko2016approx,konidaris2007building,hauskrecht1998hierarchical,anand2015novel,parr1998reinforcement,sutton1999between,konidaris2015constructing,Jiang2015,andre2002state}. Planning and \ac{RL} problems tackle solving for optimal behavior in \acp{MDP}.
